\documentclass{article}
\begin{document}
\title{ICBM Meeting with Advisor Greg Donahoe}
\date{2:30pm September 13. 2011}
\maketitle

\section{Attendance}
\begin{itemize}
\item Alex Nilson
\item Brett Hitchcock
\item Chaylo Laurino
\item Scott Beddall
\item Greg Donahoe
\end{itemize}

\section{Questions for Advisor}
\begin{itemize}
\item Asked Dr. Donahoe some of the questions we had for the client.
\item Dr. Donahoe didn't have any information other than what was in the presentation given during class.
\item We received copies of the presentation from Dr. Donahoe.
\item We won't have a graduate student mentor.
\item We explained our experience with a similar project, and said that we would like to try and produce a working demo by the end of the semester.
	\begin{itemize}
	\item Dr. Donahoe agreed that we could probably do that.
	\item There would still be work leftover for the follow-on team next semester.
	\end{itemize}
\item We received contact info for the client, Don Moreaux, from Dr. Donahoe.  Scott will contact client to set up a meeting.
\end{itemize}

\section{Advisor Suggestions and ``To-do''}
\begin{itemize}
\item Advisor suggested we contact to the College of Business
	\begin{itemize}
	\item Create a business plan with them as part of the project.
	\item Other teams have done it in the past.
	\end{itemize}
\item We need to create a website for our project.
	\begin{itemize}
	\item Needs to include project goal.
	\item Needs to include sponsor.
	\end{itemize}
\item We need to set team roles.
	\begin{itemize}
	\item Alex - secretery
	\item Scott - Leader/Contact
	\item Brett - website
	\item Chaylo - Budget
	\end{itemize}
\end{itemize}
\end{document}
