\documentclass{article}
\begin{document}
\title{ICBM Meeting via Skype}
\date{7:00pm September 21, 2011}
\maketitle

\section{Attendance}
\begin{itemize}
\item Alex Nilson
\item Brett Hitchcock
\item Chaylo Laurino
\item Scott Beddall
\end{itemize}

\section{Customer Requirements}
\begin{itemize}
\item We received a spreadsheet of system requirements from the client.
\item Client has divided them into several categories: "must," "iceberg," and "historical."
\item We read over the list of requirements as a group.
	\begin{itemize}
	\item Some questions came up.
	\end{itemize}
\end{itemize}


\section{Questions for Client}
\begin{itemize}
\item What exactly are PCA codes? 
	\begin{itemize}
	\item How are the generated, assigned, etc.?
	\item What sort of a format do them come in?
	\end{itemize}
\item Nomenclature.
	\begin{itemize}
	\item What is a work effort?
	\item Are PCA codes the same things as projects?
	\item Assignments, tasks, and work are different?
	\item What goes on the timesheet?
	\end{itemize}
\item I-Time
	\begin{itemize}
	\item What is I-Time
	\item How much do we need to interface with it?
	\end{itemize}
\end{itemize}

\section{Division of Labor}
\begin{itemize}
\item Each team member will work on use cases for some of the requirements.
	\begin{itemize}
	\item Requirements on lines 2-11 of the document go to Chaylo.
	\item Requirements on lines 12-21 of the document go to Alex.
	\item Requirements on lines 22-31 of the document go to Brett.
	\item Requirements on lines 32-38 of the document go to Scott.
	\end{itemize}
\end{itemize}

\section{Design Decisions}
\begin{itemize}
\item Track changes to SQL database for auditing purposes.
\item Users and login info stored in Active Directory.
\item Attach work efforts to PCA codes
\item Use a flag to mark work efforts as approved or not.
\item Can add/delete PCA codes only with certain permissions.
\item Work efforts are added to PCA codes.
\item PCA codes are found using searches or by sorting.
\end{itemize}

\section{Etc.}
\begin{itemize}
\item Having another meeting tomorrow in person at 12:30pm so we can use a whiteboard.
\end{itemize}

\end{document}
