\documentclass{article}
\begin{document}
\title{ICBM Meeting via Skype}
\date{7:00pm September 7. 2011}
\maketitle

\section{Attendance}
\begin{itemize}
\item Alex Nilson
\item Brett Hitchcock
\item Chaylo Laurino
\item Scott Beddall
\end{itemize}

\section{Github Account}
\begin{itemize}
\item Decided to get a basic account: 5 collaborators, 10 repos, \$12 per month.
\item One collaborator for each team member, one for advisor and client.
\item Github doesn't claim IP rights on things their servers.
\item Held off on buying the account; waiting to talk to client.
\end{itemize}

\section{Schedules}
\begin{itemize}
\item Everyone e-mailed their schedule to Scott
\item Scott is the team leader adn contact with the client; he'll be coordinating with the client and advisor
\end{itemize}

\section{Team Name}
\begin{itemize}
\item Idaho Cost Management
\item We couldn't come up with anything clever, but we might change it in the future
\end{itemize}

\section{Questions for Client}
\begin{itemize}
\item What platform will we be working on?
	\begin{itemize}
	\item Client mentioned Windoes Server 2003 in presentation, but we want to confirm.
	\end{itemize}
\item Will we need to provide our own work environment?
\item Will we be using IIS?  ASP?
\item Can we use software other than .NET to interface with database?
\item What kind of database?
\item Will we have a budget?
\item Scott will correspond with client
\end{itemize}

\section{Etc.}
\begin{itemize}
\item Alex will be secretery for the group.
\item Means he's responsible for typing up and maintaining minutes for the meetings.
\end{itemize}

\end{document}
