\documentclass{article}
\begin{document}
\title{ICBM Meeting with Client via Conference Call}
\date{2:30pm October 18, 2011}
\maketitle

\section{Attendance}
\begin{itemize}
\item Chaylo Laurino
\item Alex Nilson
\item Brett Hitchcock
\item Marj and the stakeholders
\end{itemize}

\section{Requirements Revision}
\begin{itemize}
\item Client will be giving us information about the data elements for employer and contract information.
\item DAT 3
	\begin{itemize}
	\item Need to include "earnings codes"
	\item Earnings codes are alphabetic codes used to tell what kind of pay - holiday, vacation, etc.
	\item Client wants to ability to add them rather than the codes being hard coded into the system
	\end{itemize}
\item DAT 5
	\begin{itemize}
	\item Only manager and administrators can create work efforts.
	\item Everyone can assign themselves to a work effort once it exists in the system.
	\end{itemize}
\item DAT 6
	\begin{itemize}
	\item Cost allocated work efforts will have a PCA code
	\end{itemize}
\item PCA 1 and 2
	\begin{itemize}
	\item Only Managers and Administrators can enter PCA codes and tie them to work efforts.
	\end{itemize}
\item DAT 7
	\begin{itemize}
	\item Typo - should be "non-work efforts"
	\end{itemize}
\item DAT 9
	\begin{itemize}
	\item Grouping of PCA codes and work efforts
	\end{itemize}
\item DAT 10
	\begin{itemize}
	\item Explained our idea of having a "history" database that records who made a change, when they made it, and what the SQL query was.
	\item Approved by client.
	\end{itemize}
\item DAT 13
	\begin{itemize}
	\item Also applies to non-work efforts.
	\end{itemize}
\item REP 2
	\begin{itemize}
	\item Itegration with I-Time has beendeclared "low priority"
	\end{itemize}
\item REP 3
	\begin{itemize}
	\item Should be compatible with database.
	\item Business objects.
	\end {itemize}
\item VEW 2 and 5
	\begin{itemize}
	\item Contributors can only view their own data.
	\item View should be persistant - the last layout they had will be the layout next time.
	\item Managers and administrators not bound by these rules.
	\end{itemize}
\end{itemize}

\section{Etc.}
\begin{itemize}
\item Gave customer update on our progress.
\end{itemize}
 
\end{document}
