\subsection{Software Requirements}

\subsubsection{PCA Requirements}

\bf{PCA-1} \\
Users with the proper permissions must be able to manually enter PCA codes in a form that meets DHW standards.\\
\paragraph{}
This provides the ability to correctly connect the PCA code(s) to work, and ensures we are correctly accounting for what costs are allocated to what work. Work can be project related, a maintenance activity, or a non-productive activity such as meeting time.\\
Status:\bfseries{In Progress}\\

\bfseries{PCA-2}\\
\paragraph{}
Users with proper permissions must be able to manually tie work effort(s) to valid PCA.\\
Description\\
Status:\bfseries{ In Progress}\\

The system must provide a mechanism for time bounding PCA codes - with the ability to "deactivate" a code prematurely and an open "end" date.\\

Must maintain an audit trail (history of changes - people, projects, and PCAs).

The system must provide a mechanism for preventing time to be allocated to expired PCA codes.

The system must allow multiple PCA to be assigned to a work effort, over the life of the effort/project.

Must be able to assign one or more PCA codes to work effort (split percent allocation across multiple PCAs which can change during life of work effort)

Must allow work to be assigned to other entities outside DHW

Must allow work to be associated with multiple divisions or the enterprise.

\subsubsection{Data Requirements}
The system shall track date specific vendor and employee/contractor information

The system shall allow for some description of work or project to be entered and attached.

The system shall be consistent with I-Time data

The system shall provide a means to replicate last week's assignments (repeating tasks can auto fill)

The system must have a method that allows staff to create work effort, and self-assign

Must be able to track work effort for resources, depending upon their assignment, that are either cost allocated or not cost allocated.

Must be able to break time out by time codes for work efforts, such as Vacation, Sick, LWOP, (match I-Time data since this is the system of record)

Users shall have the ability to close tasks and activities on their timesheet, and reopen if needed.

The system shall provide some mechanism (configurable dropdown) for  grouping of business, program, and function of work.

Audit trail data shall include the information that was updated, modified/deleted, date created, and by whom for each item determined to be auditable.

Data for staff and projects shall include the ability to store links and attachments

The system must allow for future time entry

Must prevent work efforts to exist in the system unless they are tied to a PCA code.

All data for reporting shall be extracted via external source (EDW. Excel, etc.).

Must allow users to create a view of their I-Time timesheet. 

Reports must be real-time, reliable, and accurate. Includes exports to csv, Excel. 

Must have a sort and group function that allows work effort to be grouped by application, division, manager, etc.

The system must allow a user the ability to create a custom view of the data.

Must allow users to easily size windows.

Must be able to limit view of information presented to user to what is pertinant to that user's role.

The system shall provide search/find functionality to locate work efforts, with minimal amount of navigation (task actions less than clicks/pages/dialogs)

Must authenticate to Active Directory

Must have a role-based permissions security.

The system shall allow for automated closure of time periods for PCA and work efforts, with administrator ability to manually reopen and close for edit and approval.

The system must allow each user the ability to navigate easily by logic/functional areas, ie. Staff demographics, projects, work items/areas, time entry, etc.

Must automatically display current week when entering timesheet data.

Must have notifications (via email, context) triggered by certain events such as timesheet submittal, approvals, PCA expiration. 

Users with permissions, must have the abiltiy to approve TARS weekly submittals.
